\begin{thebibliography}{99}

\bibitem{lakkaraju-2016} H. Lakkaraju, S. H. Bach, y J. Leskovec, 
``Interpretable decision sets: A joint framework for description and prediction'', en \emph{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 2016, pp. 1675--1684.

\bibitem{cortez-2014} P. Cortez, ``Student Performance'', UCI Machine Learning Repository, 2014. [Online]. Available: \href{https://doi.org/10.24432/C5TG7T}{https://doi.org/10.24432/C5TG7T}.

\bibitem{goodfellow-2016} I. Goodfellow, Y. Bengio y A. Courville. (2016). Deep Learning. MIT Press.

\bibitem{duda-2000} R. O. Duda, P. E. Hart, D. G. Stork. (2000). Pattern Recognition. 2nd Ed. Wiley Interscice. 

\bibitem{google-accuracy} Google Developers. (2023). Classification: Accuracy, Machine Learning Foundational Courses. Disponible en \href{https://developers.google.com/machine-learning/crash-course/classification/accuracy}{https://developers.google.com/machine-learning/crash-course/classification/accuracy}

\bibitem{google-roc} Google Developers. (2022). Classification: ROC curve and AUC, Machine Learning Foundational Courses. Disponible en \href{https://developers.google.com/machine-learning/crash-course/classification/roc-and-auc}{https://developers.google.com/machine-learning/crash-course/classification/roc-and-auc}

\bibitem{google-pr} Google Developers. (2022). Classification: Precision and Recall, Machine Learning Foundational Courses. Disponible en \href{https://developers.google.com/machine-learning/crash-course/classification/precision-and-recall}{https://developers.google.com/machine-learning/crash-course/classification/precision-and-recall}

\bibitem{Ignatiev-2018} Ignatiev, A., Pereira, F., Narodytska, N., Marques-Silva, J. (2018). A SAT-Based Approach to Learn Explainable Decision Sets. In: Galmiche, D., Schulz, S., Sebastiani, R. (eds) Automated Reasoning. IJCAR 2018. Lecture Notes in Computer Science(), vol 10900. Springer, Cham.  

\bibitem{samek-2019} W. Samek, G. Montavon, A. Vedaldi, L. K. Hansen, y K.-R. Müller, \emph{Explainable AI: Interpreting, Explaining and Visualizing Deep Learning}, Springer Nature, 2019.

\end{thebibliography}
